CF Registry Analysis

### 2024-03-07 Christine Chan/CF Registry/cf_registry_analysis.qmd
windows paths

```{r}
#| include: false
library(Hmisc)
library(zoo)
library(tidyverse)
library(forestmodel)
library(childsds)
library(gt)
library(gtsummary)
library(forcats)
library(labelled)
library(survival)
library(survminer)
library(knitr)
library(eulerr)
library(broom)
library(forestplot)
knitr::opts_knit$set(root.dir = "/Users/timvigers/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF/Christine Chan/CF Registry")
```

@@

```{r results='asis'}
invisible(lapply(time_varying, function(v) {
  new_f <- as.formula(paste0(
    y, "~", paste0(x[-which(x == v)], collapse = "+"),
    paste0("+", v, "*strata(tgroup)")
  ))
  cox_res_split <- coxph(new_f, data = s_split, cluster = eDWID)
  cat("\n")
  cat("####", v)
  cat("\n")
  cat("\n")
  plot_df <- tbl_regression(cox_res_split) %>%
    add_n(location = "level") %>%
    add_nevent(location = "level")%>% 
    as_tibble()
  plot_df$ll <- as.numeric(sapply(strsplit(plot_df$`**95% CI**`, ", "), "[", 1))
  plot_df$ul <- as.numeric(sapply(strsplit(plot_df$`**95% CI**`, ", "), "[", 2))
  plot_df$hr <- as.numeric(plot_df$`**log(HR)**`)
  plot_df %>%
    forestplot(
      labeltext = c(`**Characteristic**`, `**N**`, `**Event N**`, `**log(HR)**`),
      mean = "hr", lower = "ll", upper = "ul", 
      is.summary = is.na(plot_df$`**N**`)
    ) %>%
    fp_add_header(
      `**Characteristic**` = c("", "Characteristic"),
      `**N**` = c("", "N"),
      `**Event N**` = c("", "Event N"),
      `**log(HR)**` = c("", "log(HR)")
    ) %>%
    fp_add_lines() %>%
    fp_set_zebra_style("#EFEFEF", ignore_subheaders = T) %>%
    print()
  cat("\n")
  cat("\n")
}))
```

>>>>

```{r}
#| include: false
library(Hmisc)
library(zoo)
library(tidyverse)
library(forestmodel)
library(childsds)
library(gt)
library(gtsummary)
library(forcats)
library(labelled)
library(survival)
library(survminer)
library(knitr)
library(eulerr)
library(broom)
library(forestplot)
switch(Sys.info()[["sysname"]],
  Windows = {
    home_dir <- "C:/Users/Tim/OneDrive - The University of Colorado Denver/Vigers/CF/Christine Chan/CF Registry"
  },
  Darwin = {
    home_dir <- "/Users/timvigers/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF/Christine Chan/CF Registry"
  }
)
knitr::opts_knit$set(root.dir = home_dir)
```

@@

```{r results='asis'}
invisible(lapply(time_varying, function(v) {
  new_f <- as.formula(paste0(
    y, "~", paste0(x[-which(x == v)], collapse = "+"),
    paste0("+", v, "*strata(tgroup)")
  ))
  cox_res_split <- coxph(new_f, data = s_split, cluster = eDWID)
  cat("\n")
  cat("####", v)
  cat("\n")
  cat("\n")
  plot_df <- tbl_regression(cox_res_split) %>%
    add_n(location = "level") %>%
    add_nevent(location = "level") %>%
    as_tibble()
  plot_df$ll <- as.numeric(sapply(strsplit(plot_df$`**95% CI**`, ", "), "[", 1))
  plot_df$ul <- as.numeric(sapply(strsplit(plot_df$`**95% CI**`, ", "), "[", 2))
  plot_df$hr <- as.numeric(plot_df$`**log(HR)**`)
  plot_df %>%
    forestplot(
      labeltext = c(`**Characteristic**`, `**N**`, `**Event N**`, `**log(HR)**`),
      mean = "hr", lower = "ll", upper = "ul",
      is.summary = is.na(plot_df$`**N**`)
    ) %>%
    fp_add_header(
      `**Characteristic**` = c("", "Characteristic"),
      `**N**` = c("", "N"),
      `**Event N**` = c("", "Event N"),
      `**log(HR)**` = c("", "log(HR)")
    ) %>%
    fp_add_lines() %>%
    fp_set_zebra_style("#EFEFEF", ignore_subheaders = T) %>%
    print()
  cat("\n")
  cat("\n")
}))
```
